\LARGE A double-sampling extension of the German National Forest Inventory for design-based small area regression estimation of timber volume resources on forest district levels \\ \vspace{2ex} \large Large scale application to the federal state of Rhineland-Palatinate \vspace{-1ex}

### 2018-01-25 Draft_Form/tex/Results.tex
update 25_01_2018
update 25_01_2018 (begin Results)

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
%\subsection{Model Validations}
%\label{sec:modval_res}

>>>>

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Feasibility of estimations}
\label{sec:feasest}

% Alternative section title: General estimation results

% NOTES:
% - 1) address feasibility of estimations for each estimator
% - 2) give general overview about estimation results (see Breidenbach) before going into more detail
%
%

\newpage
% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Estimation errors}
\label{sec:esterr}

\begin{figure}[H]
	\centering
	\resizebox{1\hsize}{!}{\includegraphics{fig/error_distr_foa_fu.png}}
	\caption{Cumulative distribution of estimation errors under the simple random sampling (SRS), the pseudo small (PSMALL), the extended pseudo synthetic (EXTPSYNTH) and the pseudo synthetic (SYNTH) estimator. \textit{Left}: Results for the 45 FA units. \textit{Right}: Results for the 388 (SRS), 321 (PSMALL / EXTPSYNTH) and 403 (PSYNTH) FR units.}
	\label{fig:disterrors}
\end{figure}

\newpage
% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Gain and Relative Efficiency}
\label{sec:gain_releff}

\begin{figure}[H]
	\centering
	\resizebox{0.7\hsize}{!}{\includegraphics{fig/compare_onephase_psmall.png}}
	\caption{Cumulative distribution of variance reduction by the PSMALL compared to the SRS estimator for the  45 FA and 321 FR units.}
	\label{fig:gain}
\end{figure}

\newpage
% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
\subsection{Comparison of PSMALL and EXTPSYNTH}
\label{sec:comp}

\begin{figure}[H]
	\centering
	\resizebox{1\hsize}{!}{\includegraphics{fig/psmall_vs_extpsynth_fu.png}}
	\caption{\textit{Left}: Comparison of the g-weight variance between the PSMALL and the EXTPSYNTH estimator for the 321 FR units.
		      \textit{Right}: Difference in g-weight variance between the PSMALL and the EXTPSYNTH estimator in dependence of the terrestrial data ($n2G$) in the FR unit.}
	\label{fig:compvar}
\end{figure}

% ----------------------------------------------------------------------- %
% ----------------------------------------------------------------------- %
%\subsection{Effect of Model Accuracy}
%\label{sec:modacc_eff}
